method

### 2022-06-01 06_Paper/ER-ED/method.Rmd

library(here)       # to set directories without defined paths
# set top level directory to source file
here::i_am("flag_project_root_CERED.txt")

@@

The online survey will contain a number of questionnaires. In the focus of the current project is the Flexible Emotion Regulation Scale (FlexER)[@Doerfel2019].  
It assess flexible use of ER strategies with items such as "If I want to feel less negative emotions, I have several strategies to achieve this." 
The items are rated on a 4-point scale ranging from "strongly agree" to "strongly disagree".

@@

```{r DesignERED, echo = FALSE, message = FALSE, warning = FALSE, fig.cap = "Block design of the paradigm. Every participant starts with two \"active viewing\" blocks continaing neutral (Block 1) and negative (Block 2) pictures. Order of the regulation blocks (Blocks 3, 4, and 5) is randomized between participants. After, the discounting procedure takes place. All three regulation strategies are pairwise compared. Before the last block, participants can decide which regulation strategy they want to reapply. Subjective arousal and effort ratings are assessed after each block using a slider on screen with a continuous scale."}
include_graphics(here("06_Paper", "ER-ED", "Revision", "figures", "Design_ER-ED.png"))
```

>>>>

library(here)       # to set directories without defined paths
# set top level directory to source file
here::i_am("flag_project_root_CAD.txt")

@@

The online survey will contain a number of questionnaires. 
In the focus of the current project is the Flexible Emotion Regulation Scale (FlexER)[@Doerfel2019].  
It assess flexible use of ER strategies with items such as "If I want to feel less negative emotions, I have several strategies to achieve this.", which we define as ER flexibility. 
The items are rated on a 4-point scale ranging from "strongly agree" to "strongly disagree".

@@

```{r DesignERED, echo = FALSE, message = FALSE, warning = FALSE, fig.cap = "Block design of the paradigm. Every participant starts with two \"active viewing\" blocks continaing neutral (Block 1) and negative (Block 2) pictures. Order of the regulation blocks (Blocks 3, 4, and 5) is randomized between participants. After, the discounting procedure takes place. All three regulation strategies are pairwise compared. Before the last block, participants can decide which regulation strategy they want to reapply. Subjective arousal and effort ratings are assessed after each block using a slider on screen with a continuous scale."}
include_graphics(here("06_Paper", "ER-ED", "figures", "Design_ER-ED.png"))
```
